The Asteroseismic Imprints of Mass Transfer

### 2024-04-08 paper/paper_AA.tex

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{paper/figures/HRD_binary_compromise.pdf}
    \caption{Hertzsprung-Russell diagram showing the evolution of the binary. Tracks are coloured by the mass loss and mass accretion rate for the donor (marked D1-5) and accretor (marked A1-4), see Section~\ref{sec:hrd} for an explanation of the labels. We limit the accretion on the companion to $0.5 \, {\rm M_\odot}$ and follow its further evolution until core hydrogen exhaustion, see Section~\ref{sec:model_setup} for details on the technical implementation. For reference, we show single star tracks as dashed light grey curves, with masses from $3$ to $4 \, {\rm M_\odot}$ in $0.1 \, {\rm M_\odot}$ intervals.\\Interactive plot available online \href{www.tomwagg.com/html/interact/mass-gainer-asteroseismology.html\#fig1}{\faChartArea}.}
    \label{fig:hrd}
\end{figure}

@@

The evolution of the donor (starting at D1) initially follows the 4$\,{\rm M_\odot}$ single star track, expanding across the main sequence, exhausting core hydrogen and moving across the Hertzsprung gap. During the expansion on the Hertzsprung gap, at point D2, the donor overflows its Roche-lobe and diverges from the single star track. As it loses mass, it is driven out of thermal equilibrium. It decreases in luminosity as a fraction of the photons produced deep inside are now used to do work to expand the outer layers.  The orbit shrinks slightly at first, but quickly starts to widen \citep{Renzo+2019:2019A&A...624A..66R}. At point D3 the donor star is still transferring mass but it starts to regain thermal equilibrium. At point D4 the donor has lost its entire hydrogen-rich envelope and contracts within its Roche-lobe. It keeps contracting until it ignites helium at the point marked D5, where it resides a compact subdwarf. \referee{As noted in Section~\ref{sec:model_setup}, we limit the accretion onto the companion to $0.5 \, {\rm M_\odot}$. Although the donor continues to transfer mass beyond this point, none of this mass is accreted by the companion. Therefore, after $0.5 \, {\rm M_\odot}$ has been accreted we illustrate the track of the donor with a a grey line given it no longer impacts our accretor model, which is the focus of this work.}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{paper/figures/HRD_binary_compromise.pdf}
    \caption{Hertzsprung-Russell diagram showing the evolution of the binary. Tracks are coloured by the mass loss and mass accretion rate for the donor (marked D1-5) and accretor (marked A1-4), see Section~\ref{sec:hrd} for an explanation of the labels. We limit the accretion on the companion to $0.5 \, {\rm M_\odot}$ and follow its further evolution until core hydrogen exhaustion, see Section~\ref{sec:model_setup} for details on the technical implementation. We note the point at which $0.5 \, {\rm M_\odot}$ of material has been accreted by the accretor with a black plus sign. For reference, we show single star tracks as dashed light grey curves, with masses from $3$ to $4 \, {\rm M_\odot}$ in $0.1 \, {\rm M_\odot}$ intervals. Interactive plot available online \href{www.tomwagg.com/html/interact/mass-gainer-asteroseismology.html\#fig1}{\faChartArea}.}
    \label{fig:hrd}
\end{figure}

@@

The evolution of the donor (starting at D1) initially follows the 4$\,{\rm M_\odot}$ single star track, expanding across the main sequence, exhausting core hydrogen and moving across the Hertzsprung gap. During the expansion on the Hertzsprung gap, at point D2, the donor overflows its Roche-lobe and diverges from the single star track. As it loses mass, it is driven out of thermal equilibrium. It decreases in luminosity as a fraction of the photons produced deep inside are now used to do work to expand the outer layers.  The orbit shrinks slightly at first, but quickly starts to widen \citep{Renzo+2019:2019A&A...624A..66R}. At point D3 the donor star is still transferring mass but it starts to regain thermal equilibrium. At point D4 the donor has lost its entire hydrogen-rich envelope and contracts within its Roche-lobe. It keeps contracting until it ignites helium at the point marked D5, where it resides a compact subdwarf. \referee{As noted in Section~\ref{sec:model_setup}, we limit the accretion onto the companion to $0.5 \, {\rm M_\odot}$. Although the donor continues to transfer mass beyond this point, none of this mass is accreted by the companion and thus does not affect our accretor model. We mark this point on the donor's evolutionary track with a grey circle and highlight the rest of the track in grey.}
